Big Ideas in Sports Analytics and Statistical Tools for their Investigation

### 2022-11-07 response_to_reviewers.Rmd

## Major comments from Reviewer 2

> While Sections 2 and 3 are well done and complete, Sections 4 and 5 are weak and seem incomplete and unpolished.

As noted above, Sections 4 and 5 are significantly stronger in this revision.

> Likewise the Opportunities section should be expanded to include the proliferation of Sports Analytics conferences.

We thank the reviewer for this suggestion. We have added two paragraphs on sports analytics conferences to Section 6.

### 2022-11-07 sports_analytics.Rmd
conferences; close #41

Public research in sports analytics is driven in part by several notable competitions. 
These competitions have been an important source of new ideas and have contributed to the diversification of the field by breaking down barriers to entry.

@@

>>>>

Public research in sports analytics is driven in part by several notable competitions and conferences. 
These venues have been an important source of new ideas and have contributed to the diversification of the field by breaking down barriers to entry.

@@

The biennial [New England Symposium on Statistics in Sports](https://www.nessis.org/) is likely the longest-running academic conference devoted to sports analytics. 
It's West Coast counterpart is [The Cascadia Symposium on Statistics in Sports](http://www.cascadiasports.com/). 
Many influential results have been showcased for the first time at these conferences. 
Other prominent sports analytics conferences include the  [Carnegie Mellon Sports Analytics Conference](https://www.stat.cmu.edu/cmsac/conference/2022/), [UConn Sports Analytics Symposium](https://statds.org/events/ucsas2022/), and [MathSport International](http://www.mathsportinternational.com/).

The highest-profile sports analytics conference is undoubtedly the [Sloan Sports Analytics Conference](https://www.sloansportsconference.com/), which draws academics, industry professionals, vendors, and media organizations.
While the conference holds a research competition and has certainly drawn attention to sports analytics, it has also been criticized for a variety of shortcomings. 
These criticisms include a lack of emphasis on reproducibility in the research competition, high ticket prices, the large salaries taken by the organizers, and the lack of diversity among attendees and presenters [@funt2022].
